---
title: "The price of being a smoker"
subtitle: "Analysing insurance data of smokers and non-smokers"
author: "Federspiel Sven"
date: '2022-01-09'
output:
  pdf_document: default
  html_document: default
---
  
```{r setup, include = FALSE}
library(dplyr)
library(tidyverse)
library(tidyr)
library(ggplot2)
library(renv)
```
  
# Introduction

For this Project we will have a look at the insurance data of smokers and non-smokers from https://www.kaggle.com/mirichoi0218/insurance which shows us how expensive smoking realy is.

# The data


```{r}
data <- read_csv("insurance.csv")
data
```

# Histogram

```{r}
data %>%
 ggplot() +
  geom_histogram(aes(x = charges,fill = smoker)) +
  theme_minimal()
```

We can see that smokers have higher charges than non-smokers.

# Pie chart

```{r}

data2 = data.frame(sex = c("male","female"),
                   count = c(sum(data$smoker == "yes" & data$sex == "male"),
                        sum(data$smoker == "yes" & data$sex == "female")))

data2 %>% 
  ggplot() +
  geom_bar(stat="identity",aes(x = "", y = count , fill=sex)) +
  coord_polar("y", start=0) +
  ggtitle("Smokers")+
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 20)
        )

```

We can see that the majority of smokers are male.

# Scatterplot

```{r}

data %>%
  ggplot(aes(x = charges ,y = bmi, color = smoker))+
  geom_point()+
  geom_smooth(method='lm', formula= y~x)+
  theme_minimal()

```

We can see that the bmi does not seem to have much impact on charges for non-smokers, but for smokers a higher bmi means higher charges.